Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-10 paper_jasa.tex
typo

The number of evaluations required for each lineup to provide reasonable estimates of the power is determined by the variance of the estimated power. Suppose $\gamma$ denotes the conventional test power for each parameter combination shown in Table \ref{tbl:experiment_params}. Since the expected power of visual inference is very close to the power of conventional test (Figure \ref{fig:power_expected}) the proportion of successful evaluations of lineups should give a rough estimate for  $\gamma$. For a given proportion $\gamma$ it is desired to have a margin of error (ME) less than or equal to 0.05. Thus we have $ME =1.96 \sqrt{ \frac 1 n_{\gamma} \gamma(1-\gamma)} \le 0.05$ which gives us the estimation of minimum number of evaluations $$n_{\gamma} \geq \frac{\gamma(1-\gamma)}{(0.05/1.96)^2}.$$

>>>>

The number of evaluations required for each lineup to provide reasonable estimates of the power is determined by the variance of the estimated power. Suppose $\gamma$ denotes the conventional test power for each parameter combination shown in Table \ref{tbl:experiment_params}. Since the expected power of visual inference is very close to the power of conventional test (Figure \ref{fig:power_expected}) the proportion of successful evaluations of lineups should give a rough estimate for  $\gamma$. For a given proportion $\gamma$ it is desired to have a margin of error (ME) less than or equal to 0.05. Thus we have $ME =1.96 \sqrt{ \gamma(1-\gamma) / n_{\gamma} } \le 0.05$ which gives us the estimation of minimum number of evaluations $$n_{\gamma} \geq \frac{\gamma(1-\gamma)}{(0.05/1.96)^2}.$$
